IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-07 paper/extensions.tex
Minor fixes, and minor revision of clearance.

Full details with formal reduction rules can be found
in \appendixext{}.
%}

@@

\paragraph{Clearance}
%
LIO, SWAPI, and Breeze additionally provide a discretionary access
control (DAC) mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
%
This mechanisms is used to restrict a computation from allocating and
accessing data (or communicating with entities) above a specified
label, the clearance.
%
Amending our IFC language with clearance is mostly straight forward,
and, in particular, does not not affect our definitions or proofs in
any meaningful way.
%
To this end, we first extend tasks to track a clearance label
alongside the current label, and amend the core IFC language with two
new terminals for retrieving and setting this value.
%
Since this extension simply adds a per-task global mutable variable,
our security guarantees hold trivially.
%
However, this does not implement any DAC mechanism.
%
To do so, we must restrict the language with
$\mathcal{P}_\text{clearance}$.
%
This family contains always valid predicates, except for rules that
raise the current label (e.g., \textsc{I-setLabel}), perform
allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
clearance (clearance should not be arbitrarily raised).
%
These predicates use the clearance to impose DAC.
%
For instance, the predicate for \textsc{I-setLabel} prevents the
current label from being raised above the clearance (and thus permit
reads above the clearance); this predicate is given by $P = |il
canFlowTo il'|$, where |il'| is the clearance and |il| is the current
label.
%
The otters predicates are defined in a similar way and omitted for
clarity.

>>>>

Full details with formal reduction rules are provided
in \appendixext{}, but omitted here for space reasons.
%}

@@

\paragraph{Clearance}
%
Systems like LIO, SWAPI, and Breeze additionally provide a discretionary access
control (DAC) mechanism---called \emph{clearance}---at the language
level~\cite{Hritcu:2013:YIB:2497621.2498098, lio}.
%
This mechanisms is used to restrict a computation from allocating and
accessing data (or communicating with entities) above a specified
label, the clearance.
%
Amending our IFC language with clearance is straight forward,
and, can be done using our notation of a restricted language.
%
To this end, we first extend tasks to track a clearance label
alongside the current label, and amend the core IFC language with two
new terminals for retrieving and setting this value.
%
Since this extension only adds a per-task mutable variable whose value
has no influence on the system, all security guarantees still
hold, by essentially the same proofs.
%
However, this does not implement any DAC mechanism yet.
%
To do so, we can restrict the language with a family of predicates
$\mathcal{P}_\text{clearance}$:
All rules that
raise the current label (e.g., \textsc{I-setLabel}), perform
allocation (e.g., \textsc{I-sandbox} and \textsf{I-send}), or set the
clearance (clearance should not be arbitrarily raised), a predicate
that uses the clearance to impose DAC is used.
%
For instance, the predicate for \textsc{I-setLabel} prevents the
current label from being raised above the clearance (and thus permit
reads above the clearance).  The predicate $P := |il
canFlowTo il'|$ achieves this restriction, where |il'| is the
clearance and |il| is the current
label.
%
The other predicates are defined in a similar way and omitted for
brevity.

TODO: provide them in the appendix, and refer to them here.

### 2014-07-07 paper/retrofit.tex
Minor fixes, and minor revision of clearance.

\paragraph{Language restrictions versus isolated sandboxes}  If you want
to create a standard programming language with information-flow control,
the usual technique is to build in restrictions (dynamic or static)
which allow noninterference to be proved.  While this is fine for toy
languages, if the language in question is an existing language, these
modifications can often require extremely intrusive, both in terms of
semantic changes and implementation changes, and it is easy to get things
wrong and permit a subtle implicit flow between different security levels.

@@

\paragraph{Stack frames versus scheduling}  A feature that is supported
by some information flow control systems is the ability to temporarily
raise one's label in order to do computation on data.  Once the
computation is finished, the label is lowered back to the original
label---a stack discipline.  Care must be taken to ensure that
information doesn't leak when the label is lowered (for example, the
parent is not allowed to inspect the result of the computation). In
fact, systems with this feature generally only achieve
termination-insensitive noninterference: if the high secrecy section
doesn't terminate, this is observable by the halted execution of the low
secrecy section.

In this paper, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a
new isolated task; a sample encoding using our language is
shown in Figure~\ref{toLabeled}.

@@

The sequential processing of these
tasks corresponds to a specific \emph{scheduling policy} of these
threads.  This change of perspective to scheduling highlights the
essential differents between termination-insensitive and termination-sensitive
noninterference.

>>>>

\paragraph{Language restrictions versus isolated sandboxes}  If you want
to create a standard programming language with information-flow control,
the usual technique is to build in restrictions (dynamic or static)
which allow non-interference to be proved.  While this is fine for toy
languages, if the language in question is an existing language, these
modifications can often require extremely intrusive, both in terms of
semantic changes and implementation changes, and it is easy to get things
wrong and permit a subtle implicit flow between different security levels.

@@

\paragraph{Stack frames versus scheduling}  A feature that is supported
by some information flow control systems is the ability to temporarily
raise one's label in order to do computation on data.  Once the
computation is finished, the label is lowered back to the original
label---a stack discipline.  Care must be taken to ensure that
information doesn't leak when the label is lowered (for example, the
parent is not allowed to inspect the result of the computation). In
fact, systems with this feature generally only achieve
termination-insensitive non-interference: if the high secrecy section
doesn't terminate, this is observable by the halted execution of the low
secrecy section.

In this paper, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a
new isolated task; a sample encoding using our language is
shown in Figure~\ref{fig:toLabeled}.

@@

The sequential processing of these
tasks corresponds to a specific \emph{scheduling policy} of these
threads.  This change of perspective to scheduling highlights the
essential differents between termination-insensitive and termination-sensitive
non-interference.
